*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-23 Code/Manuscript_O2.Rmd
Added reference link to PURPAR figure
edit text

Figures \@ref(fig:MED4OverlayPlots), \@ref(fig:SS120OverlayPlots) and
\@ref(fig:MIT9313OverlayPlots) provide visual representations of the Photosynthetic Usable Radiation (PUR), the black solid line and shaded area, in relation to the imposed Photosynthetic Active
Radiation (PAR), the dotted line, under each imposed spectral wavebands for *P. marinus* MED4, SS120 and MIT9313, respectively. A complete list of absorbed PUR (µmol photons m^-2^ s^-1^) for all imposed spectral wavebands, PAR and photoperiod regimes, can be found in Table \@ref(tab:PURTable).

>>>>

Figures \@ref(fig:MED4OverlayPlots), \@ref(fig:SS120OverlayPlots) and
\@ref(fig:MIT9313OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P. marinus* MED4, SS120 and MIT9313, respectively. Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated absorbed PUR versus imposed PAR for each *P. marinus* and each spectral waveband.
